\documentclass[11pt]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{mathrsfs}
\usepackage[colorlinks = true, citecolor=red]{hyperref}
\usepackage{comment}
\usepackage{xcolor}
\usepackage{amsfonts}
\usepackage[
citestyle = authoryear
]{biblatex}
\addbibresource{Note.bib}


\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{example}{Example}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newcommand{\lemmaautorefname}{Lemma}

\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand\inner[2]{\langle #1, #2 \rangle}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\conv}{conv}

\newcommand{\R}{\mathbb{R}}
\newcommand{\Prob}[1]{\mathscr{P}_{#1}}
%opening
\title{Non-convex optimisation convex envelopes and Fenchel Conjugates}
\author{Andrew Wu}

\begin{document}
	
	\maketitle
	
	\section{Introduction}
	This note aims to extend propositions from \cite{Bauschke2010} and \cite{Tardella} to a class of optimization problems on Hilbert spaces with non-convex constraints.
	
	\begin{comment}
	\section{Problem}
	Let $X,Y$ be Hilbert spaces and suppose $f:X\times Y\to\R$ is a smooth convex function and  $g:X\times Y\to\R$ is non-convex. We want to solve the following problem, denoted by $\Prob{0}$
	\begin{equation*}
		\inf_{x,y\in X\times Y} f(x,y)
		\end{equation*}
	subject to the constraint 
	\[	g(x,y) \geq 0.
		\]
	\end{comment}
	\section{Superadditivity of convex envelopes}
	\begin{definition}
		Let $V$ be a convex subset of arbitrary space $X$ and suppose $f:X\to[-\infty,\infty]$. The convex envelope of $f$, $\conv(f):V\to[-\infty,\infty]$, is the largest convex minorant of $f$. That is, for any convex function $g:V\to[-\infty, \infty]$ such that $g\leq f$, $g\leq \conv(f)$.
		\end{definition}
	\begin{definition}
		Let $V$ be a vector space. The functional $g:V\to\R$ is affine if there exists linear functional $l:V\to\R$ and $b\in V$ such that for all $v\in V$, 
		\[  g(v) = l(v) + b
		\]
		If $l$ is a continuous linear functional, then $g$ is a continuous affine functional.
	\end{definition}
	%Proposition of Tardella generalised to arbitrary vector spaces.
	\noindent The following proposition extends \textbf{Proposition 2.20} of \cite{Tardella} from convex subsets of $\R^{n}$ to general vector spaces.
	
	\begin{theorem}
		\label{prop:conv}
		Let $V$ be a vector space. Suppose $f,g:V\to\R$ are arbitrary functionals. Then, 
		\[  \conv(f) + \conv(g)\leq \conv(f+g).
		\]
		If $g$ is affine, then 
		\[  \conv(f) + \conv(g) = \conv(f + g)
		\]
	\end{theorem}
	
	
	\begin{proof}
		Observe that $\conv(f) + \conv(g)$ is a convex underestimator of $f + g$. Hence, by definition,
		\[  \conv(f) + \conv(g)\leq \conv(f+g).
		\]
		Suppose $g$ is affine, then both $g$ and $-g$ are convex. Thus, $\conv(g) = g$ and $\conv(-g)=g$. Hence,
		\[	\conv(f + g) - g = \conv(f+g) + \conv(-g) \leq \conv(f),
				\]
		so 
		\[	\conv(f) + \conv(g) \geq \conv(f + g).
				\]
		Combining this with the first part of the proposition yields the desired equality.
		\end{proof}
	
	%\noindent \textcolor{red}{\textbf{Note:}} The condition that $V$ is a vector space guarantees $V$ is convex. 
	
	\section{Superadditivity of biconjugates}
	A similar proposition can be proved for biconjugates. 
	\begin{definition}
		Let $H$ be a Hilbert Space and $f:H\to[-\infty, \infty]$. The Fenchel conjugate (or convex conjugate or Legendre Transform) is the function $f^{*}:H\to[-\infty, \infty]$
		
		\[	f^{*}(x^*) = \sup_{x\in X} \left\{		\langle x^{*}, x\rangle - f(x)
													\right\}
				\]
		
		\noindent The biconjugate of $f$ is the function $f^{**} := (f^*)^*$.
		\end{definition}
	
	\begin{lemma}
		\label{lem:biconjugatelsc}
		Let $H$ be a Hilbert space and $f:H\to[-\infty, \infty]$. Then, $f^{**}$ is the largest convex lower semicontinuous minorant of $f$. That is, for any convex lower semicontinuous function $g$ such that $g\leq f$, $g\leq f^{**}$.
		\end{lemma}
	
	\begin{proof}
		See \textbf{Proposition 4.1} of \cite{Ekeland}.
		\end{proof}
	
	\begin{theorem}
		Let $H$ be a Hilbert space and $f,g:H\to\R$ be arbitrary functionals. Then, 
		
		\[	f^{**} + g^{**} \leq (f+g)^{**}.
		\]
		
		\noindent In particular, if $g$ is affine continuous, then 
		
		\[	f^{**} + g^{**} = (f+g)^{**}
		\]
	\end{theorem}
	
	\begin{proof}
		By \autoref{lem:biconjugatelsc}, $f^{**}, g^{**}$ are convex and lower semicontinuous and $f\leq f^{**}$, $g\leq g^{**}$. Observe that $f^{**} + g^{**}$ is a convex minorant of $f + g$, and is also lower semicontinuous by the superadditivity of the infimum. Hence, by definition, 
		\[	f^{**} + g^{**} \leq (f+g)^{**}.
				\]
		Now, if $g$ is affine and continuous, both $g$ and $-g$ are convex and lower semicontinuous. Hence, by \autoref{lem:biconjugatelsc}, $g^{**} = g$ and $(-g)^{**} = -g$, so
		\[	(f+g)^{**} - g = (f+g)^{**} + (-g)^{**}\leq f^{**},
				\]
		which rearranges to 
		\[	(f + g)^{**} \leq f^{**} + g^{**}.
				\]
		Combining this with the first inequality in the theorem yields the equality.
	\end{proof}
	
	\section{Separable additivity of biconjugates}
	
	\begin{definition}
		Let $X$ be some space. The function $f:X\to[-\infty, \infty]$ is proper if $f(x)\neq -\infty$ for all $x\in X$ and there exists $x\in X$ such that $f(x) < +\infty$.
		\end{definition}
	\begin{definition}
		Let $(X,\langle, \rangle)$ be a real Hilbert space. The functional $f:X\to[-\infty,\infty]$ has a continuous affine minorant if there exists $a\in X$ and $b\in\R$ such that for all $x\in X$:
		
		\[	f(x)\geq \langle a, x \rangle + b
				\]
		\end{definition}
	
	\begin{lemma}
		\label{lem:proper_affine}
		Let $(X,\langle, \rangle)$ be a real Hilbert space and suppose $f:X\to[-\infty, \infty]$ is proper and has a continuous affine minorant. Then, both $f^{*}, f^{**}:X\to[-\infty, \infty]$ are also proper and have affine minorants.
		\end{lemma}
	
		\begin{proof}
			See \textbf{Lemma 2.1} of \cite{Klein}
			\end{proof}
	
	\noindent The following theorem is essentially a double application of \textbf{Proposition 13.30} of \cite{Bauschke2010} where extra conditions are imposed to guarantee $g^{**}$ is proper. The proof follows that of \textbf{Theorem 2.1} in \cite{Klein} albeit with a modified definition of proper function to match \cite{Bauschke2010}. As with \cite{Bauschke2010}, we allow $\sup\{\cdot\}$ to take values $\pm\infty$. 
	
	
	\begin{theorem}
		Let $X_{1}, X_{2}, \ldots X_{n}$ be real Hilbert spaces with inner products $\langle ,\rangle_{i=1,2\ldots n}$ respectively and $X = X_{1}\times X_{2}\times \ldots X_{n}$.
		Suppose $g:X\to(-\infty,\infty]$ is a proper separable function defined by
		
		\[	g(x) = \sum_{i=1}^{n}g_{i}(x_i), \quad\text{for any }x=(x_1, x_2, \ldots, x_n)\in X,
		\]
		where  $g:X:=$ $g_{i}:X_{i}\to(-\infty, \infty]$, $i=1,2,\ldots n$ are proper functions with continuous affine minorants. Then, $g^{**}$ is proper and for all $x\in X$,
		\[	g^{**}(x) = \sum_{i=1}^{n} g_{i}^{**}(x_i),
		\]
		where $g^{**}_{i}$ are proper functions.
		\end{theorem}
		
		\begin{comment}
		\textbf{Notes:}
		\begin{enumerate}
		\item Proof of separability of $g^{*}$ is adapted from \textcolor{red}{Proposition 13.30} of Bauschke ``Convex analysis and monotone operator theory in Hilbert Spaces.''
		
		\item We allow $\sup = +\infty$ since we are dealing with functions on the extended reals. This also means we do not need to worry about the sets $\{\langle x_i^{*}, x_i\rangle - g_{i}(x_i)\}$ being bounded above, hence additivity of the $\sup$ should always hold.  
		\end{enumerate}
		\end{comment}
	
	\begin{proof}
		%Example 2.1, pg 28, Bauschke
		Let $x = (x_1, \ldots x_n)$ and $y = (y_1, \ldots y_n)$ be elements of $X$. Observe that $X$ equipped with the inner product 
		
		\[	\langle x, y\rangle := \sum_{i=1}^{n} \langle x_{i}, y_{i}\rangle_{i}
				\]
				
		\noindent defines a Hilbert space. 	Computing the Fenchel conjugate, we obtain:
		\begin{align*}
			g^{*}(x^{*}) 
			& = \sup_{x\in X}\left\{ 
									\langle x^*, x\rangle - g(x)
												\right\} \\
				%Note; here we allow supremum to take +\infty
			& = \sup_{x_1,x_2\ldots x_n} \left\{
										\sum_{i=1}^{n} \langle x^{*}_{i}, x_i\rangle - g_{i}(x_i)
												\right\}	\\
				%https://math.stackexchange.com/questions/2814076/can-you-explain-the-intuition-of-tom-apostols-proof-of-the-additive-property-of
			& = \sum_{i=1}^{n}	\sup_{x_i\in X_i} \left\{\langle x^{*}_{i}, x_i\rangle - g_{i}(x_i)\right\} \\
			& = \sum_{i=1}^{n} g_{i}^{*}(x_i)					
			\end{align*}
			
			\noindent Observe that $g^{*}$ is separable and $g_{i}^{*}:X_{i}\to[-\infty, \infty]$ are proper with continuous affine minorants by \autoref{lem:proper_affine}. Thus, reapplying the above line of reasoning yields 
			\[	g^{**}(x) = \sum_{i=1}^{n} g_{i}^{**}(x_i),
			\]
			where again, $g^{**}_{i}$ are proper by \autoref{lem:proper_affine}. Finally, if $g_{i}$, $i=1,2\ldots n$ have continuous affine minorants $\langle a_{i}, x\rangle + b_{i}$, then $\langle \sum_{i=1}^{n}a_i, x_i\rangle + \sum_{i=1}^{n} b_{i}$ is a continuous affine minorant of the proper function $g$, so $g^{**}$ is proper by \autoref{lem:proper_affine}.
		\end{proof}
		%\newpage
		\section{Subdifferentials of separable functions}
		This section gives a simple lemma connecting the total and partial subdifferentials of additively separable functions.
		\begin{lemma}
			 Suppose $X_i$, $i=1,2\ldots n$ is a family of real Hilbert spaces with inner products $\inner{\cdot}{\cdot}_i$ and denote the product Hilbert space by $\bm{X}=\bigoplus_{i=1}^{n}X_i$ (that is $\prod_{i=1}^{n}X_i$ with inner product $\sum_{i=1}^{n}\inner{\cdot}{\cdot}_i$). Let $f:\bm{X}\to\R$ be an additively separable function;
			\[  f(\bm{x}) = \sum_{i=1}^{n}f_{i}(x_i),
			\]
			where $f_i:X_i\to\R$. Let $\bm{x}=(x_1, \ldots x_n)\in\text{dom }f$. As with \cite{Bauschke2010}, we define $R_i:X_i\to \bm{X}$ such that the j$^{\text{th}}$ component of $R_i y$ is $y$ if $j=i$ and $x_j$ otherwise. Then, if $u_i\in\partial_i f(\bm{x})$ for $i=1,2,\ldots n$, then $\bm{u}=(u_1, \ldots, u_n)\in\partial f(\bm{x})$.
			\end{lemma}
		 \begin{proof}
			By definition, for all $i=1,2,\ldots n$ and $y_i\in X_i$,
			\begin{align*}
				& \inner{y_i - x_i}{u_i}_i + (f\circ R_i)(x_i)\leq (f\circ R_i)(y_i)\\
				& \inner{y_i - x_i}{u_i}_i + \sum_{j=1}^{n}f(x_j) \leq f(y_i) + \sum_{j\neq i}^{n}f(x_j) \\
				& \inner{y_i - x_i}{u_i}_i + f(x_i) \leq f(y_i).
			\end{align*}
			Adding these inequalities together, we have that for all $\bm{y}\in\bm{X}$, 
			\begin{align*}
				& \sum_{i=1}^{n}\inner{y_i - x_i}{u_i}_i + \sum_{i=1}^{n}f(x_i) \leq \sum_{i=1}^{n}f(y_i) \\
				& \inner{\bm{y} - \bm{x}}{\bm{u}} + f(\bm{x}) \leq f(\bm{y}),
			\end{align*}
			thus, $\bm{u}\in \partial f(\bm{x})$.
		\end{proof}
	\printbibliography
\end{document}